Using VDMS to Search 100M Images: A Piece of Cake

### 2020-02-18 yfcc100m/paper/vldb2020/eval.tex
Update query figures

To evaluate the access to metadata and images,
we use the following four queries, modeled after our internal use cases:
\begin{enumerate}
\item {\bf {\em 1tag}}: Find metadata/images with 1 specific autotag (i.e. alligator, lake, etc).
\item {\bf {\em 1tag\_resize}}: Find metadata/images with 1 specific autotag and resize to 224x224.
\item {\bf {\em 1tag\_resize\_geo}}: Find metadata/images with 1 specific autotag, resize to 224x224, and in a particular geolocation (with a 20 degrees radius in latitude and longitude).
\item {\bf {\em 2tag\_resize\_geo}}: Find metadata/images with 2 specific tags (i.e. alligator AND lake) and resize to 224x224.
\end{enumerate}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/queries_throughput_56}
\caption{Queries - Throughput - 56 Clients}
\label{fig:q_throughput_56}
\end{figure}

>>>>

To evaluate the access to metadata and images,
we use the following four queries, modeled after our internal use cases:
\begin{itemize}
\item Query 1 - {\bf {\em 1tag}}: Find metadata/images with 1 specific autotag (i.e. alligator, lake, etc).
\item Query 2 - {\bf {\em 1tag\_resize}}: Find metadata/images with 1 specific autotag and resize to 224x224.
\item Query 3 - {\bf {\em 1tag\_resize\_geo}}: Find metadata/images with 1 specific autotag, resize to 224x224, and in a particular geolocation (with a 20 degrees radius in latitude and longitude).
\item Query 4 - {\bf {\em 2tag\_resize\_geo}}: Find metadata/images with 2 specific tags (i.e. alligator AND lake) and resize to 224x224.
\end{itemize}

@@

% \begin{figure}[t!]
% \centering
% \includegraphics[width=\columnwidth]{figures/queries_throughput_56}
% \caption{Queries - Throughput - 56 Clients}
% \label{fig:q_throughput_56}
% \end{figure}

\begin{figure*}[ht]
\begin{subfigure}{.5\linewidth}
  \centering
  % include first image
  \includegraphics[width=\columnwidth]{figures/queries_throughput_56_q1_q2}
  \caption{Query 1 (red), and Query 2 (blue).}
  \label{fig:q1_q2}
\end{subfigure}
\begin{subfigure}{.5\linewidth}
  \centering
  % include second image
  \includegraphics[width=\columnwidth]{figures/queries_throughput_56_q3_q4}
  \caption{Query 3 (red), and Query 4 (blue).}
  \label{fig:q3_q4}
\end{subfigure}
\caption{Queries - Throughput - 56 Clients}
\label{fig:q_throughput_56}
\end{figure*}
